What's hot and what's not:\\Windowed developer topic analysis

### 2009-04-12 lda-paper.tex
et al stuff

In order to infer or associate the expertise of an author with topics
extracted from SCS, Linstead et al. proposed an author-source-code model
using LDA~\cite{10.1109/MSR.2007.20}%,NIPS2007637,1321709}. 
This model
is essentially an extension of the author-topic (AT)
model~\cite{1036902}, which associated authors and topics extracted
with LDA.

>>>>

In order to infer or associate the expertise of an author with topics
extracted from SCS, Linstead et al.\  proposed an author-source-code model
using LDA~\cite{10.1109/MSR.2007.20}%,NIPS2007637,1321709}. 
This model
is essentially an extension of the author-topic (AT)
model~\cite{1036902}, which associated authors and topics extracted
with LDA.
